---
title: "Myanmar Township Visualizations: Rakhine"
author: "SCBI Conservation GIS Lab"
date: "May 1, 2018"
output: pdf_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}

################# Modified version of Myanmar_table.R. #########################
#This script is used to generated a pdf of deforestation rates over time in townships of Myanmar.
#Please see Myanmar_table.R for source code and more detailed commentary.
#contact klingesd@si.edu for info.
```


## Contents
- Each figure represents the loss of forested area, per township, for the region of Rakhine.
- Figures are sorted in descending order (greatest to least) by amount of total forest loss
(expressed as a % of the total forest cover in 2000)
- X-axis corresponds to years 2001-2016.
- Y-axis corresponds to amount of deforested area in a given year, expressed as a % of the total
forest in 2000 (e.g., 0.03 = 3% of forest area in year 2000 lost in given year)
- Color scale stretched from green (0% loss) to red (>1%); midpoint of color scale set at
0.55% (mean forest loss for all years in all townships)



##### Correspondents
Qiongyu Huang, SCBI Conservation GIS Lab

huangq@si.edu

David Klinges, SCBI Conservation GIS Lab

klingesd@si.edu

*******
\pagebreak

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Install and call
setwd('Z:/Interns/David/Myanmar/ArcMap_working_folder/Myanmar_townships')

Sys.setenv(JAVA_HOME='C:/Program Files (x86)/Java/jre1.8.0_162')

#install.packages('dplyr', repos = 'https://cran.r-project.org/web/packages/dplyr/index.html')
#install.packages('tidyr', repos = 'https://cran.r-project.org/web/packages/tidyr/index.html')
#install.packages('ggplot2', repos = 'https://cran.r-project.org/web/packages/ggplot2/index.html')
#install.packages('data.table', repos = 'https://cran.r-project.org/web/packages/data.table/index.html')
#install.packages('rmarkdown', repos = 'https://cran.r-project.org/web/packages/rmarkdown/index.html')
#install.packages('tinytex', repos = 'https://cran.r-project.org/web/packages/tinytex/index.html')
#devtools::install_version("rmarkdown", version = "1.8", repos = "http://cran.us.r-project.org")
#install.packages('scales', repos = 'https://cran.r-project.org/web/packages/scales/index.html')
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(tidyr)
library(data.table)
library(rmarkdown)
library(tinytex)
library(scales)
```

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = FALSE
)
```


```{r, echo=FALSE, warning=FALSE}
#Objective:
#Plot the temporal change of deforestation in each township
#Automate this process, as so many townships
#Independent: year
#Dependent: % of total forest area in 2000 lost
#Title each plot to make township, state, and total forest area in 2000 apparent


#Load data: deforestation in Myanmar as determined by Hansen 2016
#Deforestation is given in Landsat pixels (30m x 30m)
Myanmar_table = read.csv("towndeforestation_total.csv")

#Change column names
Myanmar <- setnames(Myanmar_table, old = c(7:22), new = c("2016", "2015", "2014", "2013",
                                                          "2012", "2011", "2010", "2009",
                                                          "2008", "2007", "2006", "2005",
                                                          "2004", "2003", "2002", "2001"))

pix_to_km2 <- function(x) {x * 900 / 1000000} #Convert pixels to km2
km2_to_acre <- function(x) {x * 247.105} #Convert km2 to acres

#Myanmar <- mutate(Myanmar, treecover2000_km2 = sapply(select(Myanmar, 23), pix_to_km2))


#In order to determine an appropriate Y-axis scale for deforestation, sort data by amount of loss
loss <- gather(Myanmar, "Year", "Loss", 7:22)
lossper <- mutate(loss, Loss = Loss / treecover2000)
lossper <- arrange(lossper, Loss)

#Calculate average amount of forest loss in a given year, for all townships
lossmean <- mean(lossper$Loss)

#Add column for percent loss
Myanmar <- mutate(Myanmar, percentloss = totalloss/treecover2000)

#Sort table by Region and then district
Myanmar.sorted <- arrange(Myanmar, Region, desc(percentloss))

#Separate table by region

region_list <- list("Ayeyarwady", "Bago", "Chin", "Kachin", "Kayah", "Magway", "Mandalay", "Mon", "Naypyitaw", "Sagaing", "Shan", "Tanintharyi", "Yangon", "Rakhine")


Ayeyarwady <- filter(Myanmar.sorted, Region == "Ayeyarwady")
Bago <- filter(Myanmar.sorted, Region == "Bago")
Chin <- filter(Myanmar.sorted, Region == "Chin")
Kachin <- filter(Myanmar.sorted, Region == "Kachin")
Kayah <- filter(Myanmar.sorted, Region == "Kayah")
Magway <- filter(Myanmar.sorted, Region == "Magway")
Mandalay <- filter(Myanmar.sorted, Region == "Mandalay")
Mon <- filter(Myanmar.sorted, Region == "Mon")
Naypyitaw <- filter(Myanmar.sorted, Region == "Naypyitaw")
Sagaing <- filter(Myanmar.sorted, Region == "Sagaing")
Shan <- filter(Myanmar.sorted, Region == "Shan")
Tanintharyi <- filter(Myanmar.sorted, Region == "Tanintharyi")
Yangon <- filter(Myanmar.sorted, Region == "Yangon")
Rakhine <- filter(Myanmar.sorted, Region == "Rakhine")
```

```{r, echo = FALSE, warning=FALSE}
plotfun <- function(i) {

    #Subset to a particular row
    township <- slice(Rakhine, i)
    
    #Create variables for strings that will be referenced later
    town <- as.character(township$Township)
    district <- as.character(township$District)
    region <- as.character(township$Region)
    forest2000 <- formatC(
                  (sapply(township$treecover2000, km2_to_acre)),
                  format = "e", digits = 2)
    totalloss <- formatC(
                  (sapply(township$totalloss, km2_to_acre)),
                  format = "e", digits = 2)
    
    #Create new data frame of just two columns, the year, and the amount of
    #forest loss (expressed as a % of total forest in 2000)
    township <- gather(township, "Year", "Loss", 7:22)
    township <- mutate(township, Loss = Loss / treecover2000)
    township <- select(township, Year, Loss)
    
    #Turn into a data frame (is this necessary? who knows)
    township <- data.frame(township)
    
    township$Year <- as.integer(township$Year)
    
    #Create plot
    plot <- ggplot(township, aes(x = Year, y = Loss, fill = Loss)) +
      geom_col() +
      scale_fill_gradient2(low = '#003300', high = '#990000', mid = '#eae43f',
                           midpoint = lossmean, limits = c(0, .011), oob = squish) +
      ylab("Deforested Area as % of Forest Cover in 2000") +
      coord_cartesian(xlim = NULL, ylim = c(0.00, 0.03), expand = TRUE) +
      theme(axis.text.x = element_text(size = 10)) +
      theme(axis.text.y = element_text(size = 14)) +
      theme(axis.title.x = element_text(size = 16, face = 'bold')) +
      theme(axis.title.y = element_text(size = 12, face = 'bold')) + 
      scale_x_continuous(breaks=seq(2001, 2016, 5 )) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
            panel.background = element_blank(), axis.line = element_line(colour = "black")) +
      theme(plot.title = element_text(size = 16)) +
      labs(title = paste('Forest Loss,', town, 'in', district, 'of', region),
           subtitle = paste('Total Deforestation =', totalloss, 'acres;', 'Total Forest in 2000 =', forest2000, 'acres'))

    if ((summarise(township, max(Loss))) > 0.03) {
      plot <- plot + coord_cartesian(xlim = NULL, ylim = 
                                       c(0.00, as.numeric(summarise(township, max(Loss)))), expand = TRUE)}

    #Save plot to list
    return(plot)
}

# Loop tasks over all 286 township rows
for (i in (1:nrow(Rakhine))) {
  plot(plotfun(i))
}
```

